---
title: "Overview"
author: "Chinmay Mandal"
date: "January 12, 2017"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Overview of the FARS package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, include = FALSE}
library(Assignment3.2.1)
library(dplyr)
library(maps)
```

This vignette gives an overview of the Assignment3.2.1. The package is designed to analyze FARS data.

## Package functions

Following are exported functions:

- `fars_read()`
- `fars_summarize_years()`
- `fars_map_state()`

For example purpose data on FARS can be found in `\extdata` folder.

## Read from a CSV file
The function `fars_read()` can be used to read from a csv file.validates the file path and abort the process if the path is incorrect with an error message. This function returns a data frame of records.


```{r fars_read_example}
filename <- system.file("extdata/accident_2013.csv.bz2", package = "Assignment3.2.1")
fars_read(filename)
```

## Summarize accident cases

The function `fars_summarize_years()` takes a list of years and based on the data, a summary of accidents occured in a given month and year is prepared. The input file should be present in data folder inside working directory.

```{r fars_summarize_years_example}
setwd(system.file("extdata", package = "Assignment3.2.1"))
fars_summarize_years(2013:2015)
```

## Plotting accident locations on map

The function `fars_map_state()` helps to plot the accident hit location on map. It takes two input the satate number and year.


```{r fars_map_state_example}
setwd(system.file("extdata", package = "Assignment3.2.1"))
fars_map_state(45, 2015)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
